\chapter{Subcellular Localisation of IFIT Proteins in the Context of RSV Inclusion Bodies} \label{ch:Subcellular Localisation of IFIT Proteins in the Context of RSV Inclusion Bodies}
\section{Background and Aims} \label{sec:Background and Aims-Chapter3}
Add intro about what we think it's happening with IBs and pIBs
Using pIBs as simpler model (only N+P+ cellular components) -> h/bRSV infections -> overexpression during infection

First aim: look at how does cellular and subcellular localisation changes in response to infection, which could suggest ivolvement of IFITs with RSV lifecycle
Second aim: detaily asses the interaction of IFITs and RSV IBs during infection, with a foollow up experiments on a simplified system of pIBs, along with overexpression during infection, to further assess these



\section{Results} \label{sec:Results-Chapter3}
\input{08. Chapter 3/Subchapters/01. Localisation intorduction.tex}
\input{08. Chapter 3/Subchapters/02. Infection.tex}
\input{08. Chapter 3/Subchapters/03. pIB.tex}
\input{08. Chapter 3/Subchapters/04. Overexpression.tex}

\section{Conclusions} \label{sec:Conclusions-Chapter3}
pIBs and IBs are dynamic structures and that's why we see variable interactions within the same IFIT experiments.

transfecting bi2f24 + bngfp + p inhibits bpIBs (compared to hi2f or bi2f)









% random notes that will be useful later
IBs containing visible IBAGs were significantly larger than those without 6.4 µm2 versus 2.3 µm2 (Rincheval et al., 2017)
Although small IBs (≤2.5 μm2) were observed as early as 6 h p.i., they did not colocalize with detectable levels of p65 (FJ thesis)
Our pseudo-IBs were also mostly spherical and at 24 h post-transfection, measured up to 6.9 μm2 , which is considerably less than that of the conventional IBs observed in infected cells. (FJ thesis)
Visible aggregates measured above 3 µm2 with the average size increasing as infection progressed (Fig 4.5B). At 48 h p.i., p65 aggregations had a mean area of 22.18 µm2 but smaller puncta (<10 µm2 ) were also observed, most likely the result of nascent infections in nearby cells. (FJ thesis)
Their mean area also increased to 8.99 µm2 by 24 h p.i. (FJ thesis)
At 48 h p.i., p65 aggregations had a mean area of 22.18 µm2 but smaller puncta (<10 µm2 ) were also observed, most likely the result of nascent infections in nearby cells (FJ thesis)

stuff we tried but did not work: 
inf-transf bi1, hi3, bi5
pib with hi2f and i3-ha (ha signal not strong enough or trasnfection didnt work)
pib in 293t for other ifits (cells were dying and falling off)
hif2 and bovine pIB
experiments with human I2 RBM
in general bovine pIBs
hI2F with bRSV
