\chapter{Acknowledgements}
First, I would like to sincerely thank my supervisors, Dr Dalan Bailey and Dr Trevor Sweeney, for their exceptional guidance and unwavering support throughout the project. Thank you both for your empathy and understanding, creating an environment that fostered both academic and personal growth. I am profoundly grateful to Dalan for his exceptional mentorship, encouragement, and his compassionate, human approach, which has had a great impact on this journey. 

In addition, I would like to thank all past and present members of the Viral Glycoproteins group at the Pirbright Institute: Dr James Kelly, Dr Fatoumatta Jobe, Nazia Thakur, Leanne Logan, Dr Carina Conceição, Emily Lacey, Dr Stacey Human, Ahmed Mohamed, Dr Giulia Gallo, and  Dr Joseph Newman, who have been an invaluable source of support from the start of my PhD. The collaborative spirit within the labs has created a remarkable atmosphere that has significantly enriched my research experience. Special thanks for the enjoyable lunch breaks and the wonderful team spirit and the tremendous help that has made this not only productive but also fun.

Secondly, I am grateful to Prof. Ian Brierley, who kindly took me on midway through my PhD and has been supportive in ensuring a smooth transition. Your insightful contributions and invaluable academic guidance has helped me navigate the final phases of the thesis. I would also like to thank to members of other labs at the Virology Division at the University of Cambridge, for the positive and collaborative spirit, creating a welcoming atmosphere.

The work contained within this thesis would not have been possible without the support of the core facilities teams at the Bioimaging Facilities at both the Department of Pathology and the Pirbright Institute, for which I am incredibly grateful. I also need to thank the Department of Pathology and the Pirbright Institute for funding my studentship and giving me this opportunity.

To my friends, both in Slovakia and abroad, thank you for keeping me sane throughout this journey. Special thanks to my housemates in the Selwyn house and other Cantabrigian friends for creating a home that was not only a fun and relaxing place but also a haven during both highs and lows. Thank you for all the dinners, walks around Grandchester and musical extravaganzas. Thank you especially to Albi and Darius for the endless nights of briscola, ice-cream making, and aperitechnos.

Lastly, to my wife Cristina, your unwavering support, understanding, and patience have been my enduring foundations. You have been my colleague, friend, partner in crime, and the pillar that has kept me going through the brightest days and darkest times. I am profoundly grateful for your presence in my life.

A heartfelt thank you goes to my family, including my sister, brother, and especially my parents, Katka and Marek, for their support throughout my entire life. Their belief in me and encouragement to pursue my passions have been instrumental. \textbf{Ďakujem vám za všetko!}

\begin{figure}[b]
$$\mbox{"Started making it. Had a breakdown. Bon Appetite" - James Acaster}$$
\end{figure}

% Words in text: 484