\chapter{Assessment of Transcriptional Induction of Human IFITs in the Context of RSV} \label{ch:Assessment of Transcriptional Induction of Human IFITs in the Context of RSV}
\section{Background and Aims} \label{sec:Background and Aims-Chapter 1}
As discussed in Section \ref{sec:Interferon-Induced Proteins with Tetratricopeptide Repeats}, the \textit{IFIT} gene family are interferon-stimulated genes (ISGs) that are generally activated early in the antiviral response. Their transcription is mainly regulated via interferon-stimulated response elements (IRSE), activated by ISGF3 and interferon regulatory factors (IRF) 3 and 7 (Figure \ref{fig:Pathways Inducing ISG mRNA Production.}). In short, these are activated downstream of interferon receptor signalling cascades, and via intracellular and extracellular recognition of PAMPs. As mentioned in Section \ref{subsec:IFIT Responses to Viral Infections}, human IFITs are also known to restrict a plethora of viruses. The examples include IFIT1 and IFIT3 restriction of PIV3 \cite{Rabbani2016Identification3}, and more significantly IFIT1, IFIT2 and IFIT3 restriction of human RSV \cite{Drori2020InfluenzaProteins}. In the latter, it was shown that overexpression of these IFITs negatively affects human RSV replication kinetics, while the silencing of \textit{hIFIT1}, \textit{hIFIT2}, and \textit{hIFIT3} caused the opposite effect. Clearly, IFITs seem to have an important role in the RSV life cycle which should be investigated further. It is not known, however, if \textit{hIFITs} are indeed induced following RSV infection and thus able to negatively influence RSV replication in homeostatic pathophysiological conditions.

We hypothesised human \textit{IFITs} to be induced by human RSV infection, which would allow them to enact their antiviral roles as previously shown in the literature. We aimed to systematically test this by initially confirming that our model cell lines are capable of IFIT induction following treatment with known innate immune system activators such as interferons, LPS (extracellular PAMP), and transfection with poly I:C (intracellular PAMP). These assays also allowed us to decipher which innate immune response pathways are responsible for \textit{IFIT} induction. Further, we assessed \textit{IFITs} induction by hRSV as a function of concentration and duration of infection. Lastly, we investigated the potential of species cross-protection by assessing \textit{hIFIT} induction by bovine RSV infection. All data was also validated in more physiologically relevant cell lines. 

\section{Results} \label{sec:Results-Chapter 1}
\input{06. Chapter 1/Subchapters/01. human induction}

\section{Conclusions} \label{sec:Conclusions Chapter 1}
Our experiments reveal the induction of human \textit{IFITs} in both A549 and BEAS2B cell lines, albeit with a more moderate response observed in BEAS2B. The induction trends are summarised in Table \ref{tab:Summary of Human IFIT Responses to Activators of Innate Immune Response.}. Further literature research uncovered that the BEAS2B cell line maintains higher basal expression of interferon-stimulated genes, providing a potential explanation for our observations \cite{Seng2014HighResistance}. Notably, both cell lines exhibit a time-dependent response to IFN$\upalpha$ stimulation in an inverse manner, indicating that \textit{hIFITs} are acute responders to IFN$\upalpha$ treatment. Interestingly, the varying induction magnitudes of \textit{IFITs} between the cell lines reveals that while \textit{IFIT5} shows the lowest induction levels in both cell lines, A549 has \textit{IFIT1} as the highest-induced IFIT, contrasting with BEAS2B, where \textit{IFIT2} was induced to the highest level. Additional A549 experiments demonstrate that LPS incubation stimulates \textit{IFIT} induction, but the magnitude, especially in comparison to other stimulants, appears biologically insignificant. Remarkably, IFN$\upgamma$ consistently elicits \textit{IFIT} induction in a concentration-independent manner, manifesting a uniform induction magnitude across various \textit{IFITs}—a characteristic not observed with other stimulants. Initially, these results were surprising, given our assumption that IFN$\upgamma$-mediated signalling was pertinent only to myeloid cell lines, a classification the A549 cell line does not fall under. However, published evidence on IFN$\upgamma$ receptor expression more broadly across cell types \cite{Ivashkiv2018IFN:Immunotherapy} and, more specifically, transcriptomic data in the A549 cell line reported in the Human Protein Atlas \cite{Uhlen2015Tissue-basedProteome}, corroborate the presence of IFN$\upgamma$ receptor expression in A549 cells. Moreover, transfected poly I:C induces \textit{IFITs} to levels surpassing those elicited by other tested innate immune system stimulants.

\begin{table}
    \centering
    \begin{tabular}{lllll}
    \hline
        \textbf{Cell Line} & \textbf{IFIT} & \textbf{Treatment} & \textbf{Figure} & \textbf{Trend} \\ \hline
        A549 & IFIT1 & hIFN$\upalpha$ 1000 IU 6h & Figure 3.1 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT1 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.1 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT1 & hIFN$\upgamma$ 500 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT1 & hIFN$\upgamma$ 1000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT1 & hIFN$\upgamma$ 2000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT1 & LPS 5 ng/mL 6h & Figure 3.3 & \(\nearrow\) \\ 
        A549 & IFIT1 & LPS 5000 ng/mL 6h & Figure 3.3 & \(\nearrow\) \\ 
        A549 & IFIT1 & poly I:C 2 µg 24h & Figure 3.4 & \(\uparrow\)\(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT1 & hIFN$\upalpha$ 1000 IU 3h & Figure 3.5 & \(\rightarrow\) \\ 
        BEAS2B & IFIT1 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.5 & \(\nearrow\) \\ 
        A549 & IFIT2 & hIFN$\upalpha$ 1000 IU 6h & Figure 3.1 & \(\uparrow\) \\ 
        A549 & IFIT2 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.1 & \(\uparrow\) \\ 
        A549 & IFIT2 & hIFN$\upgamma$ 500 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT2 & hIFN$\upgamma$ 1000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT2 & hIFN$\upgamma$ 2000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT2 & LPS 5 ng/mL 6h & Figure 3.3 & \(\nearrow\) \\ 
        A549 & IFIT2 & LPS 5000 ng/mL 6h & Figure 3.3 & \(\uparrow\) \\ 
        A549 & IFIT2 & poly I:C 2 µg 24h & Figure 3.4 & \(\uparrow\)\(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT2 & hIFN$\upalpha$ 1000 IU 3h & Figure 3.5 & \(\searrow\) \\ 
        BEAS2B & IFIT2 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.5 & \(\uparrow\) \\ 
        A549 & IFIT3 & hIFN$\upalpha$ 1000 IU 6h & Figure 3.1 & \(\uparrow\) \\ 
        A549 & IFIT3 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.1 & \(\uparrow\) \\ 
        A549 & IFIT3 & hIFN$\upgamma$ 500 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT3 & hIFN$\upgamma$ 1000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT3 & hIFN$\upgamma$ 2000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT3 & LPS 5 ng/mL 6h & Figure 3.3 & \(\nearrow\) \\ 
        A549 & IFIT3 & LPS 5000 ng/mL 6h & Figure 3.3 & \(\uparrow\) \\ 
        A549 & IFIT3 & poly I:C 2 µg 24h & Figure 3.4 & \(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT3 & hIFN$\upalpha$ 1000 IU 3h & Figure 3.5 & \(\rightarrow\) \\ 
        BEAS2B & IFIT3 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.5 & \(\uparrow\) \\ 
        A549 & IFIT5 & hIFN$\upalpha$ 1000 IU 6h & Figure 3.1 & \(\nearrow\) \\ 
        A549 & IFIT5 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.1 & \(\nearrow\) \\ 
        A549 & IFIT5 & hIFN$\upgamma$ 500 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT5 & hIFN$\upgamma$ 1000 IU 6h & Figure 3.2 & \(\nearrow\) \\ 
        A549 & IFIT5 & hIFN$\upgamma$ 2000 IU 6h & Figure 3.2 & \(\uparrow\) \\ 
        A549 & IFIT5 & LPS 5 ng/mL 6h & Figure 3.3 & \(\nearrow\) \\ 
        A549 & IFIT5 & LPS 5000 ng/mL 6h & Figure 3.3 & \(\uparrow\) \\ 
        A549 & IFIT5 & poly I:C 2 µg 24h & Figure 3.4 & \(\uparrow\) \\ 
        BEAS2B & IFIT5 & hIFN$\upalpha$ 1000 IU 3h & Figure 3.5 & \(\rightarrow\) \\ 
        BEAS2B & IFIT5 & hIFN$\upalpha$ 1000 IU 24h & Figure 3.5 & \(\nearrow\) \\ \hline
    \end{tabular}
    \caption[Summary of Human \textit{IFIT} Responses to Activators of Innate Immune Response.]{\textbf{Summary of Human \textit{IFIT} Responses to Activators of Innate Immune Response.} Trend arrows indicate abundance relative to mock-treated values: strong downregulation ($\downarrow$, 0.062-0.25); mild downregulation ($\searrow$, 0.25-0.5); no difference ($\rightarrow$, 0.5-1.5); mild upregulation ($\nearrow$, 1.5-4); moderate upregulation ($\uparrow$, 4-64); strong upregulation ($\uparrow\uparrow$, 64-258); very strong upregulation ($\uparrow\uparrow\uparrow$, 258-1024).}
    \label{tab:Summary of Human IFIT Responses to Activators of Innate Immune Response.}
\end{table}

Further, we confirmed that high MOI hRSV infection, but not low MOI infection, induces \textit{hIFIT} expression. The summary of all human \textit{IFIT} responses to hRSV infection can be seen in Table \ref{tab:Summary of Human IFIT Responses to hRSV Infection.}. We observed a concentration and time-dependent effect, which was maintained for at least 48 HPI, for all \textit{hIFITs} but \textit{hIFIT1}, which nevertheless showed the most robust induction out of all the genes tested. We confirmed that this induction isn't due to cellular contaminants from the viral preparation step, as infecting cells with purified virus induced similar patterns of gene expression. In A549, this induction was greatly diminished following pharmacological blockage of the interferon receptor, and completely abolished by UV-inactivation of hRSV, indicating the necessity of RSV replication for the initial \textit{IFIT} induction and functional interferon signalling for a robust \textit{IFIT} response. Most likely infected cells initiate an innate immune response, which also induces \textit{IFIT} locally and results in interferon production. This is then sensed by surrounding cells by paracrine interferon signalling, which in turn prophylactically induces \textit{IFIT} in those cells. This data was mirrored in the BEAS2B cell line, with minor discrepancies in the overall magnitude of \textit{IFIT} induction—aligning with the induction potential by hIFN$\upalpha$ and apparent \textit{IFIT} downregulation in cells infected with hRSV while the interferon receptor was pharmacologically inhibited. This sµggests the requirement of basal interferon sensing for the observed basal \textit{IFIT} expression in mock-treated cells. Intriguingly, the induction observed by transfection of poly I:C wasn't observed when infecting cells with hRSV while inhibiting the interferon receptor, hinting at the induction during poly I:C transfection being caused by subsequent interferon signalling, not solely internal foreign nucleic acid detection.

\begin{table}
    \centering
    \begin{tabular}{lllll}
    \hline
        \textbf{Cell Line} & \textbf{IFIT} & \textbf{Treatment} & \textbf{Figure} & \textbf{Trend} \\ \hline
        A549 & IFIT1 & hRSV MOI 0.1 24 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT1 & hRSV MOI 0.1 48 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT1 & hRSV MOI 1 24 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT1 & hRSV MOI 1 48 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT1 & hRSV MOI 2 24 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT1 & hRSV MOI 2 48 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT1 & purified hRSV MOI 1 24 HPI & Figure 3.7 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT1 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.7 & $\uparrow$ \\ 
        A549 & IFIT1 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.7 & $\rightarrow$ \\ 
        BEAS2B & IFIT1 & purified hRSV MOI 1 24 HPI & Figure 3.8 & $\uparrow$ \\ 
        BEAS2B & IFIT1 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.8 & $\downarrow$ \\ 
        BEAS2B & IFIT1 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.8 & $\rightarrow$ \\ 
        A549 & IFIT2 & hRSV MOI 0.1 24 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT2 & hRSV MOI 0.1 48 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT2 & hRSV MOI 1 24 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT2 & hRSV MOI 1 48 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT2 & hRSV MOI 2 24 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT2 & hRSV MOI 2 48 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT2 & purified hRSV MOI 1 24 HPI & Figure 3.7 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT2 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.7 & $\uparrow$ \\ 
        A549 & IFIT2 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.7 & $\rightarrow$ \\ 
        BEAS2B & IFIT2 & purified hRSV MOI 1 24 HPI & Figure 3.8 & $\uparrow$ \\ 
        BEAS2B & IFIT2 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.8 & $\rightarrow$ \\ 
        BEAS2B & IFIT2 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.8 & $\rightarrow$ \\ 
        A549 & IFIT3 & hRSV MOI 0.1 24 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT3 & hRSV MOI 0.1 48 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT3 & hRSV MOI 1 24 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT3 & hRSV MOI 1 48 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT3 & hRSV MOI 2 24 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT3 & hRSV MOI 2 48 HPI & Figure 3.6 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT3 & purified hRSV MOI 1 24 HPI & Figure 3.7 & $\uparrow$$\uparrow$ \\ 
        A549 & IFIT3 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.7 & $\uparrow$ \\ 
        A549 & IFIT3 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.7 & $\rightarrow$ \\ 
        BEAS2B & IFIT3 & purified hRSV MOI 1 24 HPI & Figure 3.8 & $\uparrow$ \\ 
        BEAS2B & IFIT3 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.8 & $\downarrow$ \\ 
        BEAS2B & IFIT3 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.8 & $\rightarrow$ \\ 
        A549 & IFIT5 & hRSV MOI 0.1 24 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT5 & hRSV MOI 0.1 48 HPI & Figure 3.6 & $\rightarrow$ \\ 
        A549 & IFIT5 & hRSV MOI 1 24 HPI & Figure 3.6 & $\nearrow$ \\ 
        A549 & IFIT5 & hRSV MOI 1 48 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT5 & hRSV MOI 2 24 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT5 & hRSV MOI 2 48 HPI & Figure 3.6 & $\uparrow$ \\ 
        A549 & IFIT5 & purified hRSV MOI 1 24 HPI & Figure 3.7 & $\uparrow$ \\ 
        A549 & IFIT5 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.7 & $\rightarrow$ \\ 
        A549 & IFIT5 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.7 & $\rightarrow$ \\ 
        BEAS2B & IFIT5 & purified hRSV MOI 1 24 HPI & Figure 3.8 & $\uparrow$ \\ 
        BEAS2B & IFIT5 & purified hRSV MOI 1 24 HPI with ruxolitinib & Figure 3.8 & $\downarrow$ \\ 
        BEAS2B & IFIT5 & purified UV inactivated hRSV MOI 1 24 HPI & Figure 3.8 & $\rightarrow$ \\ \hline
    \end{tabular}
     \caption[Summary of Human \textit{IFIT} Responses to hRSV Infection.]{\textbf{Summary of Human \textit{IFIT} Responses to hRSV Infection.} Trend arrows indicate abundance relative to mock-treated values: strong downregulation ($\downarrow$, 0.062-0.25); mild downregulation ($\searrow$, 0.25-0.5); no difference ($\rightarrow$, 0.5-1.5); mild upregulation ($\nearrow$, 1.5-4); moderate upregulation ($\uparrow$, 4-64); strong upregulation ($\uparrow\uparrow$, 64-258); very strong upregulation ($\uparrow\uparrow\uparrow$, 258-1024).}
    \label{tab:Summary of Human IFIT Responses to hRSV Infection.}
\end{table}

The summary of human \textit{IFIT} responses to bRSV infection can be seen in Table \ref{tab:Summary of Human IFIT Responses to bRSV Infection.}. In A549, both bRSV WT and mutants induced \textit{hIFIT} expression, irrespective of the presence or absence of SH, NS1, or NS2 proteins. Notably, very low MOI $\Updelta$NS infections induced \textit{hIFIT}, contrary to low MOI hRSV infection. The observations of high magnitude \textit{hIFIT} induction, and following observations from hRSV infections, sµggest bRSV-mediated \textit{hIFIT} mRNA expression increase being mediated by viral replication and paracrine interferon signalling. Intriguingly, the BEAS2B cell line exhibited \textit{IFIT} induction only in $\Updelta$NS2 and double mutant $\Updelta$NS1/2 bRSV, sµggesting BEAS2B ISGs' insensitivity to bRSV infection, unlike what was observed in the A549 cell line. As discussed in Section \ref{subsec:The Function of RSV Proteins}, NS1 and NS2 proteins can both distrupt the homeostasis of host innate immune response. Both proteins are required for the formation of "Nonstructural degradosome complex", which degrades numerous proteins involved in the innate immune system \cite{Boyoglu-Barnum2019BiologyDevelopment.}, while NS2 can interfere with the activation of IRF3 through its interaction with RIG-I, inhibiting the activation of IFN response genes \cite{Wright2006TheHumans}; and NS1 exhibiting a more individual role, such as interacting and interfering with the gene regulatory domains of immune response genes in the nucleus, or inhibiting the MAVS-RIG-1 complex formation on mitochondrial membranes \cite{Sedeyn2019RespiratoryResponses, Spann2004SuppressionMacrophages}. We have observed that the absence of NS2 protein more potently rescued the induction of \textit{hIFITs} in both A549 and BEA2B cell lines, compared to the absence of NS1 protein. In both cell lines we have observed a synergistic increase of \textit{hIFITs} mRNA levels after infection with $\Updelta$NS1/2 bRSV, suggesting both NS2 interfering with activation of IRF3, as well as the formation of a "Nonstructural degradosome complex" are involved in modulation of \textit{hIFIT} induction. Literature suggests that hRSV and bRSV are confined to their respective hosts \textit{in vivo} \cite{Buchholz2000ChimericVaccine}, potentially explained by \textit{hIFIT} induction as a result of infection, indicating that the A549 cell line more closely mimics species cross-protection expectations.

\begin{table}
    \centering
    \begin{tabular}{lllll}
    \hline
        \textbf{Cell Line} & \textbf{IFIT} & \textbf{Treatment} & \textbf{Figure} & \textbf{Trend} \\ \hline
        A549 & IFIT1 & bRSV MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT1 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT1 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT1 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.11 & \(\uparrow\) \\ 
        A549 & IFIT1 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\)\(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT1 & bRSV MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT1 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT1 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.13 & \(\rightarrow\) \\ 
        BEAS2B & IFIT1 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        BEAS2B & IFIT1 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        A549 & IFIT2 & bRSV MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT2 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT2 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\) \\ 
        A549 & IFIT2 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.11 & \(\uparrow\) \\ 
        A549 & IFIT2 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT2 & bRSV MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT2 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.12 & \(\rightarrow\) \\ 
        BEAS2B & IFIT2 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.13 & \(\rightarrow\) \\ 
        BEAS2B & IFIT2 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        BEAS2B & IFIT2 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        A549 & IFIT3 & bRSV MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT3 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.10 & \(\uparrow\)\(\uparrow\) \\ 
        A549 & IFIT3 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\) \\ 
        A549 & IFIT3 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.11 & \(\uparrow\) \\ 
        A549 & IFIT3 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.11 & \(\uparrow\)\(\uparrow\) \\ 
        BEAS2B & IFIT3 & bRSV MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT3 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT3 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.13 & \(\downarrow\) \\ 
        BEAS2B & IFIT3 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        BEAS2B & IFIT3 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.13 & \(\uparrow\) \\ 
        A549 & IFIT5 & bRSV MOI 1 24 HPI & Figure 3.10 & \(\uparrow\) \\ 
        A549 & IFIT5 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.10 & \(\uparrow\) \\ 
        A549 & IFIT5 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.11 & \(\nearrow\) \\ 
        A549 & IFIT5 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.11 & \(\nearrow\) \\ 
        A549 & IFIT5 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.11 & \(\nearrow\) \\ 
        BEAS2B & IFIT5 & bRSV MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT5 & bRSV $\Updelta$SH MOI 1 24 HPI & Figure 3.12 & \(\nearrow\) \\ 
        BEAS2B & IFIT5 & bRSV $\Updelta$NS1 MOI 0.001 24 HPI & Figure 3.13 & \(\rightarrow\) \\ 
        BEAS2B & IFIT5 & bRSV $\Updelta$NS2 MOI 0.01 24 HPI & Figure 3.13 & \(\rightarrow\) \\ 
        BEAS2B & IFIT5 & bRSV $\Updelta$NS1/2 MOI 0.001 24 HPI & Figure 3.13 & \(\nearrow\) \\ \hline
    \end{tabular}
    \caption[Summary of Human \textit{IFIT} Responses to bRSV Infection.]{\textbf{Summary of Human \textit{IFIT} Responses to bRSV Infection.} Trend arrows indicate abundance relative to mock-treated values: strong downregulation ($\downarrow$, 0.062-0.25); mild downregulation ($\searrow$, 0.25-0.5); no difference ($\rightarrow$, 0.5-1.5); mild upregulation ($\nearrow$, 1.5-4); moderate upregulation ($\uparrow$, 4-64); strong upregulation ($\uparrow\uparrow$, 64-258); very strong upregulation ($\uparrow\uparrow\uparrow$, 258-1024).}
    \label{tab:Summary of Human IFIT Responses to bRSV Infection.}
\end{table}

Another intriguing observation from this part of the study is the differential induction patterns among \textit{IFITs} when responding to stimuli. In A549, \textit{IFIT1} consistently emerges as the highest inducer, while \textit{IFIT2} and \textit{IFIT3} show similar induction patterns and magnitudes. In the BEAS2B cell line, these patterns remain fairly similar, but at times \textit{IFIT1} isn't the highest inducer. \textit{hIFIT5} seems to be consistently the worst induced IFIT in both cell lines. Notably, the maximal induction of \textit{hIFIT5} observed in this study seems 10-16 fold, an order of magnitude lower than what's observed for other \textit{hIFITs}. While the existing literature posits that IFITs should share genomic regulatory elements \cite{Lou2009IFR-9/STAT2STAT1}, our empirical data indicates potential disparities in both promoter and enhancer activities. Attempting to elucidate these distinctions, we turned to the IFIT promoters and enhancers data available in the GeneCards database \cite{Stelzer2016TheAnalyses, Fishilevich2017GeneHancer:GeneCards}. However, the intricacy of the dataset, coupled with constraints in time and expertise, impeded a comprehensive analysis. Nevertheless, our initial pre-analysis aligns with our experimental findings and sµggests that the regulation of \textit{IFIT} expression is intricate, exhibiting variability, and appears to be \textit{IFIT}-specific (data not shown).

Overall, our data sµggest that RSV infection, irrespective of species, robustly induces \textit{hIFITs}, potentially enabling them to exert antiviral activity against RSV. To validate these findings comprehensively, future studies should encompass a broader range of concentrations and treatment durations for both stimulants and RSV, while expanding the repertoire of stimulants and RSV subtypes. Additionally, increasing the number of biological replicates is crucial to minimise data variability. Including additional, more relevant cell lines and primary cells, such as patient-derived nasal tissue organoids, cultured in liquid-air interface cultures, would offer a more representative \textit{in vivo} context for selective stimulation/infection of cells relevant to RSV infection \cite{Michi2021ACells, Rajan2022TheTherapeutics}. Furthermore, our research lays the foundation for mechanistic studies on IFIT-mediated RSV inhibition. Assessing the subcellular localisation of IFIT proteins during RSV infection could provide insights into their mechanism of action. Lastly, given the limited information on the interaction with and induction by bovine RSV of bovine IFIT proteins and genes, further investigations are warranted to determine whether the observed data in human cell lines is conserved across species.






%Words in text: 6022
%Words in headers: 42
%Words outside text (captions, etc.): 1880
%total = 6064
%total with captions = 7944